Placeholder

### 2021-02-17 Paper_Histograms.Rmd
Added template code to add plot caption to the gender, age, employ, ethnicity merged retro plot

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)

@@

>>>>

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          bottom = textGrob("Grid caption", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))

bottom = textGrob("grid caption", x = 1, 
                                hjust = 1, gp = gpar(fontface = 3L, fontsize = 9)))

@@

```{r Gender age ethnicity employ retro graph with plot caption}

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))
